---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BMC

<!-- badges: start -->
<!-- badges: end -->

The goal of BMC is to classify timeseries data into one of 13 behaviours:
G: Growth
D: Decline
E: Equilibrium
GD: Growth and Decline
GE: Growth and Equilibrium
DG: Decline and Growth
DE: Decline and Equilibrium
GDE: Growth, Decline and Equilibrium
DGE: Decline, Growth and Equilibrium
OC: Oscillating Constant(ly)
OG: Oscillating Growth
OD: Oscillating Decline
OE: Oscillating Equilibrium

## Installation

You can install the development version of BMC from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Martina9Curran/BMC")
```

## Example

This is a basic example which shows you how to solve a common problem:
Please note you need to include the path to the file, it works with .csv only, but do not add .csv to the path!
```{r example}
library(BMC)
## basic example code
behaviours <- classify("C:/Users/techstaff/Desktop/packagetest/Supplementary Data/Data/check3")
```

For classification that needs more input, first check the equilibrium on your plots:
The threshold value is default at .001
If you get equilibrium when you don't want it, make the threshold smaller (eg 0, .0001)
If there is no equilibrium seen by the classifier, but you want it to be, make the threshold bigger (eg .01, .025)
```{r threshold}
classify("C:/Users/techstaff/Desktop/packagetest/Supplementary Data/Data/check3", threshold=.0001)
```

If there are problems with the behaviours (it is growing then declining, but says Decline Growth) change the attributes of the tree. This is generally the only issue with median needing to be changed, but in case of others, check the attributes that are involved in the decision of the behaviour given/required (follow the branches from the node up to the root). To change these, they are included as extra parameters in '...' and as such, are included as strings in the classify function. Note the threshold needs to be added whether or not it is being changed!
```{r attributes}
classify("C:/Users/techstaff/Desktop/packagetest/Supplementary Data/Data/check3", threshold=.001, "median")
```

Hyperparameters available for removing unwanted noise include:
"deleteStart" (Default FALSE, using this will set it to TRUE): which deletes the start of the output in the feature vector when creating attributes. It does not change the data
"keepDiscrete" (Default FALSE to help remove noise, using this will set it to TRUE, keeping all small changes in the data except for the threshold, this still works the same)

```{r numerous attributes and attributes}
classify("C:/Users/techstaff/Desktop/packagetest/Supplementary Data/Data/check3", threshold=.001, "median", "deleteStart")
```
